Predictive 3D modelling of free oblique cutting introducing an ANN-based material flow law with experimental validation over a wide range of conditions

### 2023-12-11 Article.tex
Revision in red

A 3-axis GF Mikron VCE 600 Pro milling machine is used to perform dry orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at \qty{750}{\degreeCelsius} for \qty{1}{\hour} followed by air cooling) with the same kinematics as a shaper. As shown in Figure \ref{fig:ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test). The top of the sample has 3 ribs of \qty{1}{\mm} width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} length. The test consists of removing the top layer (its height is the uncut chip thickness, $h$) of a rib at the prescribed cutting speed, $v_c$. The cutting speed is provided by the feed rate, $v_f$, of the machine (maximum value of \qty{40}{\metre\per\min}). The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample. Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times. \FD{Add comment to link with SECO's recommendations for the standard tool + reference}

>>>>

A 3-axis GF Mikron VCE 600 Pro milling machine is used to perform dry orthogonal and oblique cutting tests on Ti6Al4V (grade 5 annealed at \qty{750}{\degreeCelsius} for \qty{1}{\hour} followed by air cooling) with the same kinematics as a shaper. As shown in Figure \ref{fig:ExpSetup}, the tungsten carbide tool (modified LCGN160602-0600-FG, CP500 from SECO) is fixed on a dedicated holder (modified CFHN-06 from SECO) and the sample to be cut is clamped in the spindle (no rotation is allowed during the test). The top of the sample has 3 ribs of \qty{1}{\mm} width (the width of the tool is \qty{6}{\mm}) and \qty{10}{\mm} length. The test consists of removing the top layer (its height is the uncut chip thickness, $h$) of a rib at the prescribed cutting speed, $v_c$. The cutting speed is provided by the feed rate, $v_f$, of the machine (maximum value of \qty{40}{\metre\per\min}). The tool cutting edge inclination, $\lambda_s$, results from the relative angular orientation of the tool and the sample. Table \ref{tab:CutCond} shows the cutting conditions: 6 cutting speeds, 3 uncut chip thicknesses and 2 inclination angles, each repeated 3 times. \textcolor{red}{An inclination angle of \qty{6}{\degree} is the typical value when turning Ti6Al4V, while cutting speeds and uncut chip thicknesses values in accordance with recommended ranges by SECO for the standard tool \cite{secotoolsab_Turning_2011} are adopted.}
